
\section{Smoothness Of A Space} 
Define Moduli Of Smoothness, remark on positiveness %(cioranescu 1.3.10 using convexity)
\begin{df} %(Cioranescu 1.3.1, 1.3.9, 1.3.10)\rm 
    Let X be a seminormed space and $x_0 \in X$. 
    \begin{enumerate}
        \item We define the \bf modulus of smoothness \rm of $X$ at $x_0$, $\tilde{\rho}:[0,\infty) \times X \to \R$ by 
        \begin{equation}
            \tilde{\rho}(\epsilon,x) = \frac{1}{2} \sup\limits_{\norm{y} < 1} \pa{\norm{x+\epsilon y}+\norm{x-\epsilon y} -2\norm{x}}
        \end{equation}
        \item We define the \bf modulus of smoothness \rm of $X$, $\rho:[0,\infty) \to \R$ by 
        \begin{equation}
            \rho(\epsilon) = \sup\limits_{\norm{x} \geq 1} \rho(\epsilon, x)
        \end{equation}
        \item We say that X is \bf locally uniformly smooth \rm at $x_0$ if $\lim\limits_{\epsilon \to 0} \frac{\tilde{\rho}(\epsilon,x_0)}{\epsilon} = 0$. 
        \item We say that X is \bf locally uniformly smooth \rm if it is locally uniformly smooth at each of its points.
        \item We say that X is \bf uniformly smooth \rm if $\lim\limits_{\epsilon \to 0} \frac{\rho(\epsilon)}{\epsilon} = 0$. 
        \item  We say that X is \bf smooth \rm at $x_0$ if $Jx_0$ is a singleton.
        \item We say that X is \bf smooth \rm if it is smooth at each of its points.
        \item \ref{prop:smoothcharacterization} motivates defining $X$ to be called \bf very smooth \rm  at $x_0$ if it is smooth and $J$ is seminorm to weak continuous at $x_0$. 
        \item We say that X is \bf very smooth \rm if it is very smooth at each of its points. 
    \end{enumerate} 
\end{df}



\begin{prop}[Smooth Characterization]
    \label{prop:smoothcharacterization}
    Let $X$ be a seminormed space, $x_0 \in X$, and $J$ it's normalized duality mapping. 
    The following are equivalent. 
    \begin{enumerate}
        \item X is a smooth at $x_0$.
        \item Every selection of $J$ is norm to $weak^*$ continuous at $x_0$.
        \item There exists a selection of J which is norm to $weak^*$ continuous at $x_0$.
        \item $\norm{\cdot}$ is Gateaux Differentiable at $x_0$. 
        \item For every $y \in X$, there is a unique $\alpha \in \C$ such that $x \perp (\alpha x + y)$. 
        \item For every $y,z \in X$, if $x \perp y$ and $x \perp z$, then  $x \perp y + z$.
        \item (NEED TO DEFINE HYPERPLANE)There is a supporting hyperplane for $\overline{B_X(0;\norm{x})}$ at x. 
    \end{enumerate}
    %Cioranescu 1.3.5, 1.3.12
    %Diestel Theorem 1 p. 22
    %Diestel Theorem 4, P. 26
    %Cioranescu 1.3.6
\end{prop} 

\begin{prop}[Degrees Of Smoothness]
    \label{prop:degreesofsmoothness}
    Let $X$ be a seminormed space. 
    \begin{enumerate}
        \item If $X$ is uniformly smooth, then it is locally uniformly smooth. 
        \item If $X$ is locally uniformly smooth, then it is very smooth.
        \item If $X$ is very smooth, then it is smooth. 
    \end{enumerate} 
    %(Cioranescu 1.3.11
\end{prop} 
\begin{prop}[Very Smooth]
    \label{prop:verysmooth}
\end{prop}
\begin{prop}[Local Uniformly Smooth At A Point]
    \label{prop:localuniformlysmoothatapoint}
    Let X be a seminormed space, $x_0 \in X$, and $J$ be $X's$ normalized duality mapping. The following conditions are equivalent. 
    \begin{enumerate}
        \item X is locally uniformly smooth at $x_0$.
        \item J is continuous at $x_0$.
        \item $\norm{\cdot}$ is Frechet differentiable at $x_0$. 
    \end{enumerate} 
\end{prop} 
\begin{cor}[Local Uniformly Smooth]
    \label{cor:localuniformlysmooth}
    Let X be a seminormed space and J be $X's$ normalized duality mapping. The following conditions are equivalent.
    \begin{enumerate}
        \item X is locally uniformly smooth.
        \item J is conitnuous.
        \item $\norm{\cdot}$ is Frechet differentiable. 
    \end{enumerate} 
\end{cor} 
\begin{prop}[Uniformly Smooth]
    \label{prop:uniformlysmooth}
    Let X be a seminormed space and $J$ be $X's$ normalized duality mapping. The following are equivalent. 
    \begin{enumerate} 
        \item X is uniformly smooth. 
        \item J is uniformly continuous on bounded subsets of X. 
        \item $\norm{\cdot}$ is uniformly Frechet differentiable on bounded subsets of X.
    \end{enumerate} 
\end{prop} 
%Diestel p. 29 Lemma, P. 30 THeorem

