\chapter{Smoothness And Convexity}
\label{ch:thisChapterLabel}
\section{Convexity And Smoothness Of A Space}
\begin{prop}[Smoothness and Strict Convexity]
Let X be a seminormed space and J be $X's$ normalized duality mapping. 
\begin{enumerate} 
\item If $X^*$ is smooth, then X is strictly convex.
\item If $X^*$ is strictly convex, then X is smooth. 
\item If X is reflexive, then $X$ is strictly convex if and only if $X^*$ is smooth. 
\item If X is reflexive, then $X$ is smooth if and only if $X^*$ is strictly convex. 
\item If $X^*$ is strictly convex, then J is single valued and norm to $weak-*$ continuous. 
\item X is smooth and strictly convex if and only if J is single valued and strictly monotone. 
\end{enumerate} 
%Cioranescu 2.1.3, 2.1.4, 2.1.5, 2.1.10, 2.1.11, 2.1.12 (As corollary of 2.1.12), 
\end{prop} 

\begin{prop}[Lindenstraus Duality Formula] %2.2.12 Cioranescu (Lindenstrauss Duality Formula)
\end{prop} 
\begin{prop}[Very Smooth and Weak Local convexity]
\end{prop} 
\begin{prop}[Local Uniform Smoothness and Local Uniform Convexity]
Let X be a seminormed space and J be $X's$ normalized duality mapping. 
\end{prop} 
\begin{prop}[Uniform Smoothness and Convexity]
Let X be a (possibly complete) seminormed space and J be X's normalized duality mapping.  
\begin{enumerate}
\item X is uniformly convex if and only if $X^*$ is uniformly smooth. 
\item X is uniformly smooth if and only if $X^*$ is uniformly convex. 
\item $X^*$ is uniformly convex if and only if J is single valued and uniformly continuous on bounded subsets of X. 
\end{enumerate} 
%Cioranescu 2.2.13, 2.2.14,2.2.16)
\end{prop}
\begin{cor} Uniformly Smooth Banach Spaces are Reflexive %(Cioranescu 2.2.15) 
\end{cor}
\begin{prop}[Normalized Convergence]
Let X be a smooth locally uniformly convex seminormed space with normalized duality mapping J. If $\{x_n\}_{n \in \N} \subset X$, $x \in X$, $j_x \in Jx$, and $j_n \in Jx_n$ for each $n \in \N$, then 
\begin{equation} 
\ip{x_n-x, j_n-j} \to 0 \implies x_n \to x
\end{equation} 
\end{prop} 
%Include Diestel Corollary 1, p.32

\section{Convexity, Smoothness, and High Order Duals}
If you start with a poorly behaved Space, then things can only get worse. 

\begin{thm} %(Diestel Theorem 1 p.32)
If X is a seminormed space and $X^* $ is very smooth, then X is reflexive.
\end{thm} 

\begin{cor}
Let X be a seminormed space. 
\begin{enumerate}
\item If $X^*$'s norm is Frechet differentiable, then X is reflexive. 
\item If $X^{**}$ is weakly locally uniformly convex, then X is reflexive. 
\item If $X^{***}$ is smooth, then X is reflexive. 
\item If $X^{****}$ is strictly convex, then X is reflexive.
\end{enumerate}
\end{cor} 