\begin{prop}[\FilterConvergence Facts]
\label{prop:FilterConvergenceFacts}

\rm
    Let $(X,\scT)$ be a \TopologicalSpace. 
    Let $x \in X$. 
    Let \NeighborhoodFilterInstance{\scT}(x) denote the 
    \NeighborhoodFilter for $\scT$ at $x$. 
    Let $\scF$ be a \Filter on $X$. 
    Let $\scB$ be a \FilterBase for $\scF$. 
    The following are true. 
    \begin{enumerate}[label=(\roman*), ref={\ref{prop:FilterConvergenceFacts}.~\roman*}]
    \item 
    \label{prop:FilterConvergenceFacts:BaseEquivalence}
    $x$ is a \FilterLimit of $\scF$ if and only if $x$ is a \FilterLimit of $\scB$. 
    \item 
    \label{prop:FilterConvergenceFacts:FundamentalSystemExistence}
    $x$ is a \FilterLimit of $\scB$ if and only if, for some 
    \FundamentalSystemOfNeighborhoods $\scU$ of $x$, 
    \scNested{\scB}{\scU} holds. 
    \item 
    \label{prop:FilterConvergenceFacts:FundamentalSystemForAll}
    $x$ is a \FilterLimit of $\scB$ if and only if, 
    for every 
    \FundamentalSystemOfNeighborhoods $\scU$ of $x$, 
    \scNested{\scB}{\scU} holds. 
    \item 
    \label{prop:FilterConvergenceFacts:FinerFilter}
    If $x$ is a \FilterLimit of $\scF$ and $\scG$ is \FinerFilter
    than $\scF$ then $x$ is a \FilterLimit of $\scG$. 
    \item 
    \label{prop:FilterConvergenceFacts:CoarserTopology}
    If $x$ is a \FilterLimit of $\scF$ in $(X,\scT)$, and 
    $\scT_1$ is a \TopologyCoarser \Topology on $X$, then 
    $x$ is a \FilterLimit of $\scF$ in $(X, \scT_1)$. 
    \item 
    \label{prop:FilterConvergenceFacts:Intersection}
    Let $\{\scF_\alpha\}_{\alpha \in A}$ be a collection of 
    \Filters on $X$ each of which have $x$ as a \FilterLimit. 
    Then $\bigcap\limits_{\alpha \in A} \scF_\alpha$ has $x$
    as a \FilterLimit. 
    \item 
    \label{prop:FilterConvergenceFacts:UltrafilterCondition}
    $x$ is a \FilterLimit of $\scF$ if and only if 
    $x$ is a \FilterLimit of every $\UltraFilter$ 
    which is \FinerFilter than $\scF$. 
    \end{enumerate}
    \begin{proof}[Proof of \ref{prop:FilterConvergenceFacts:BaseEquivalence}]
       This is a direct result of 
       \ref{prop:FilterBaseFacts:FiltersAreFilterBases}. 
    \end{proof}
    \begin{proof}[Proof of \ref{prop:FilterConvergenceFacts:FundamentalSystemExistence}]
    $(\implies)$ 
    Let $x$ be a \FilterLimit for $\scB$.
    By 
    \ref{def:FilterConvergence}, 
    $\scU_{\scT}(x) \subset \scF$.
    Hence, 
    \scNested{\scF}{\scU_{\scT}(x)} holds.
    Since \Nested is 
    \TransitiveRelation 
    and 
    by 
    \ref{prop:FilterBaseFacts:BaseCondition}, 
    $\scNested{\scB}{\scU_{\scT}(x)}$ holds.
    Since $\scU_{\scT}(x)$ is a 
    \FundamentalSystemOfNeighborhoods for $x$, 
    this direction of the proof is complete. 

    $(\impliedby)$
    Let $\tilde{\scU}$ be a 
    \FundamentalSystemOfNeighborhoods
    for $x$
    such that $\scNested{\scB}{\tilde{\scU}}$ holds. 
    Then by \ref{def:FundamentalSystemOfNeighborhoods:Nesting}, 
    $\scNested{\tilde{\scU}}{\scU_{\scT}(x)}$.
    Since \Nested is 
    \TransitiveRelation 
    we conclude 
    $\scNested{\scB}{\scU_{\scT}(x)}$. 
    Since $\scB \subset \scF$, 
    $\scNested{\scF}{\scU_{\scT}(x)}$ holds. 
    By \ref{prop:FilterBaseFacts:FinerCondition}, 
    we conclude $\scU_{\scT}(x) \leq \scF$, 
    and so $x$ is a \FilterLimit of $\scB$  
    by \ref{def:FilterConvergence}.
    \end{proof}
    \begin{proof}[Proof of \ref{prop:FilterConvergenceFacts:FundamentalSystemForAll}]
    $(\impliedby)$ 
    This is a trivial consequence of the $(\impliedby)$ direction of
    \ref{prop:FilterConvergenceFacts:FundamentalSystemExistence}.
    
    $(\implies)$ 
    Let $x$ be a \FilterLimit of $\scB$. 
    Then $\scU_{\scT}(x) \subset \scF$. 
    Let $\scU$ be a 
    \FundamentalSystemOfNeighborhoods
    For $X$ at $x$. 
    By 
    \ref{def:FundamentalSystemOfNeighborhoods:AreNeighborhoods}, 
    $\scU \subset \scU_{\scT}(x)$, so 
    $\scU \subset \scU_{\scT}(x) \subset \scF$. 
    Hence $\scNested{\scF}{ \scU}$ holds. 
    Since $\scNested{\scB}{\scF}$ holds and since 
    \Nested is a \TransitiveRelation, 
    $\scNested{\scB}{\scU}$ holds. 
    \end{proof}
    \begin{proof}[Proof of \ref{prop:FilterConvergenceFacts:FinerFilter}]
    This is clear since \FilterFineness is a \PartialOrdering and is therefore \TransitiveRelation.
    \end{proof}
    \begin{proof}[Proof of \ref{prop:FilterConvergenceFacts:CoarserTopology}]
    If $\scT_1$ is \TopologyCoarser than $\scT$, then 
    $\scU_{\scT_1}(x) \subset \scU_{\scT}(x)$. 
    If $x$ is a \FilterLimit of $\scF$ in $(X, \scT)$, then 
    $\scU_{\scT}(x) \subset \scF$. 
    Hence, $\scU_{\scT_1}(x) \subset\scF$, so 
    $x$ is a \FilterLimit of $\scF$ in $(X,\scT_1)$. 
    \end{proof}
    \begin{proof}[Proof of \ref{prop:FilterConvergenceFacts:Intersection}]
    Let $U \in \scU_{\scT}(x)$. 
    Then for each $\alpha \in A$, $U \in \scF_{\alpha}$. 
    Hence $U \in \bigcap\limits_{\alpha \in A} \scF_{\alpha}$. 
    Hence 
    $\scU_{\scT}(x) \subset \bigcap\limits_{\alpha \in A} \scF_{\alpha}$. 
    so $x$ is a \FilterLimit of 
    $\bigcap\limits_{\alpha \in A} \scF_{\alpha}$.
    \end{proof}
    \begin{proof}[Proof of \ref{prop:FilterConvergenceFacts:UltrafilterCondition}]
    $(\implies)$ 
    This direction is a direct consequence of 
    \ref{prop:FilterConvergenceFacts:FinerFilter}.

    $(\impliedby)$
    By \ref{prop:UltraFilterFacts:UltrafilterIntersection}, 
    $\scF$ is the intersection of all \Ultrafilters on $X$ 
    which contain $\scF$. 
    By \ref{prop:FilterConvergenceFacts:Intersection}, if 
    these all have $x$ as a \FilterLimit, then $\scF$ must also
    have $x$ as a \FilterLimit.
    \end{proof}
\end{prop}
